Fragile Families Data Cleaning

### 2021-10-14 Reports/FFCleaning2.Rmd
05 ewas script and results section improvements

```{r sva}

@@

```{r, saveData}
save(child_base, file=paste0(datadir, 'CreatedData/', 'ChildBaseModelData.Rdata'))
save(teen_base, file=paste0(datadir, 'CreatedData/', 'ChildBaseModelData.Rdata'))
save(basemodeldata, file=paste0(datadir, 'CreatedData/', 'BaseModelData.Rdata'))

>>>>

```{r sva, eval=F}

@@

```{r saveData, eval=F}
save(child_base, file=paste0(datadir, 'CreatedData/', 'ChildBaseModelData.Rdata'))
save(teen_base, file=paste0(datadir, 'CreatedData/', 'ChildBaseModelData.Rdata'))
save(basemodeldata, file=paste0(datadir, 'CreatedData/', 'BaseModelData.Rdata'))
